---
title: "AE 5: The Office"
---

::: callout-important
Go to the [course GitHub organization](https://github.com/sta210-s22) and locate the repo titled `ae-5-the-office-YOUR_GITHUB_USERNAME` to get started.
:::

## Packages

```{r load-packages}
#| message: false

# List of packages for session
.packages = c("tidyverse","tidymodels", "knitr", "gghighlight")

# Install CRAN packages (if not already installed)
.inst <- .packages %in% installed.packages()
if(length(.packages[!.inst]) > 0) install.packages(.packages[!.inst])

# Load packages into session 
lapply(.packages, require, character.only=TRUE, quietly = TRUE)
```

## Load data

```{r}
office_ratings <- read_csv("data/office_ratings.csv")
```

## Exploratory data analysis

Recreate at least one of the exploratory visualizations from class.

## Test/train split

Split your data into testing and training sets.

## Build a recipe

Build the recipe from class.

------------------------------------------------------------------------

*Time permitting...*

## Workflows and model fitting

Build the modeling workflow and fit the model to the training data after feature engineering with the recipe.
